Paper analysis

### 2025-03-28 Paper_analysis.Rmd
update site

```{r shap_pol}
grid.arrange(
  sv_importance(ex.polbase.glb), sv_importance(ex.polmarg.glb),
  ncol = 2
)

@@

```{r shap_Nexp}
grid.arrange(
  sv_importance(ex.nexpbase.glb), sv_importance(ex.nexpmarg.glb),
  ncol = 2
)

@@

```{r shap_sed}
grid.arrange(
  sv_importance(ex.sedbase.glb), sv_importance(ex.sedmarg.glb),
  ncol = 2
)

@@

```{r shap_wb}
grid.arrange(
  sv_importance(ex.qbbase.glb), sv_importance(ex.qbmarg.glb),
  ncol = 2
)

@@

>>>>

```{r shap_pol, fig.width=9}
grid.arrange(
  sv_importance(ex.polbase.glb), sv_importance(ex.polmarg.glb),
  ncol = 2
)

Base pollinator model Shapley dependence plot. Colors are the strongest interactor with that variable.

```{r shap_pol_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.polbase.glb, v="ntr_pland"),
  sv_dependence(ex.polbase.glb, v="ann_agr_pland"), 
  ncol = 2
)

Margin pollinator model Shapley dependence plot. Colors are the strongest interactor with that variable.

```{r shap_pol_margshap}
grid.arrange(
  sv_dependence(ex.polmarg.glb, v="ntr_pland")
)

@@

```{r shap_nexp, fig.width=9}
grid.arrange(
  sv_importance(ex.nexpbase.glb), sv_importance(ex.nexpmarg.glb),
  ncol = 2
)

```{r shap_nexp_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.nexpbase.glb, v="ntr_pland"),
  sv_dependence(ex.nexpbase.glb, v="ann_agr_pland"), 
  sv_dependence(ex.nexpbase.glb, v="ntr_ed"), 
  ncol = 2
)

```{r shap_nexp_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.nexpmarg.glb, v="ntr_pland"),
  sv_dependence(ex.nexpmarg.glb, v="ann_agr_pland"), 
  sv_dependence(ex.nexpmarg.glb, v="ntr_ed"), 
  ncol = 2
)

@@

```{r shap_sed, fig.width=9}
grid.arrange(
  sv_importance(ex.sedbase.glb), sv_importance(ex.sedmarg.glb),
  ncol = 2
)

```{r shap_sed_baseshap}
grid.arrange(
  sv_dependence(ex.sedbase.glb, v="ann_agr_ed")
)

```{r shap_sed_margshap}
grid.arrange(
  sv_dependence(ex.sedmarg.glb, v="ann_agr_ed"),
  sv_dependence(ex.sedmarg.glb, v="field_frac_mn"),
  ncol=2
)

@@

```{r shap_wb, fig.width=9}
grid.arrange(
  sv_importance(ex.qbbase.glb), sv_importance(ex.qbmarg.glb),
  ncol = 2
)

@@

```{r shap_qb_baseshap}
grid.arrange(
  sv_dependence(ex.qbbase.glb, v="field_frac_mn")
)

```{r shap_qb_margshap}
grid.arrange(
  sv_dependence(ex.qbmarg.glb, v="prn_ann_ratio"),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn"),
  ncol=2
)
